Untitled

### 2024-01-03 code/analysis_Redo.Rmd
balanced panel only

  inner_join(df.spill2 %>% 
  group_by(Zip, `BHCMIS ID`) %>% 
  summarise(counts = n()) %>% 
    filter(counts == 10), by = c("Zip","BHCMIS ID"))  %>%

@@

zp.pats <- tes %>% #tes[-1,] %>% 
  cbind(Quantile = 1:8) %>% 
  ggplot(aes(x = Quantile, y = Estimate)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=Estimate-1.96*Std..Error, ymax=Estimate+1.96*Std..Error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Effects on Total Patients, by Quantile from Competitive Shock")+ xlab("Quantile of Zip Codes by Distance from Competitive Shock, adjusting for 1 year anticipation") + ylab("Effect Size")

@@

>>>>

  inner_join(df.spill2 %>% 
  group_by(Zip, `BHCMIS ID`) %>% 
  summarise(counts = n()) %>% 
    filter(counts == 10), by = c("Zip","BHCMIS ID"))  %>%
  filter(Att == 0 | Att > 2013) %>%

@@

zp.pats <- tes[-1,] %>% 
  cbind(Quantile = 1:6) %>% 
  ggplot(aes(x = Quantile, y = Estimate)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=Estimate-1.96*Std..Error, ymax=Estimate+1.96*Std..Error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Effects on Total Patients, by Quantile from Competitive Shock")+ xlab("Quantile of Zip Codes by Distance from Competitive Shock, adjusting for 1 year anticipation") + ylab("Effect Size")

@@

quantile(df.spill3[df.spill3$Att > 0,]$Dist, 1/3)
quantile(df.spill3[df.spill3$Att > 0,]$Dist, 2/3)
